### 2021-12-21 input/figdel.tex
adapting to two columns, stilltodo. simpler problem display
about example
mostly about algo text
separating issues
better plan?
meow

\begin{figure}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}\Process~$a$ deletes its
      partition.  It notifies all \processes that belong to its
      partition.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    %
    \subfloat[Part B][\label{fig:delB}$\delta$ stops as soon as they
      encounter another partition. \Process~$b$ answers with its
      partition.]{\input{input/figdelB.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    \NAMEB. $a$ eventually knows that it belongs to $P_d$.}
\end{figure}

>>>>

\begin{figure}
  \newcommand{\SCALE}{0.95}

  \newcommand{\LEFT}{\triangleleft}
  \newcommand{\RIGHT}{\triangleright}

  \begin{center}
    \subfloat[Part A][\label{fig:delA}$a$ deletes its partition. It
      notifies all \processes that belong to its
      partition.]{\input{input/figdelA.tex}}
    \hspace{3pt}
    \subfloat[Part B][\label{fig:delB}$\delta$ stops as soon as it encounters
      another partition. $b$ answers with its partition.]{\input{input/figdelB.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    scoped broadast. $a$ eventually acknowledges that it belongs to $P_d$ with $\alpha_d^3$ echoing.}
\end{figure}

### 2021-12-21 input/figsimplerproblem.tex
meow

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:problemB}Both $a$ and $c$ delete their partition 
     while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:problemD}$b$ delivers and forwards $\delta_c$. $c$
    stays in the deleted partition $P_a$.]
             {\input{input/figsimplerproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Even in the simplest scenarios, naive
    propagation of $\alpha$ and $\delta$ messages may be insufficient
    to guarantee consistent partitioning. In the bottom scenario, if
    $c$ had children, they would stay in the wrong partition
    too.

    % Despite both scenarios look the same from $c$'s perspective, $c$
    % must acknowledge $P_a$'s \emph{possible} deletion and propagate
    % it.
  }
\end{figure*}

>>>>

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:problemB}Both $a$ and $c$ delete their partition 
     while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:problemD}$\alpha_c^3$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemD.tex}}
    \hspace{5pt}
    \subfloat[Part E][\label{fig:problemE}$\delta_c$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemE.tex}}
    \hspace{5pt}
    \subfloat[Part F][\label{fig:problemF}$a$ and $b$ do not belong to any partition but
      $c$ stays forever in a stale one: $P_a$.]
             {\input{input/figsimplerproblemF.tex}}
  \end{center}
  \caption{\label{fig:problem}Even in the simplest scenarios, the
    naive propagation of $\alpha$ and $\delta$ messages may be
    insufficient to guarantee consistent partitioning. If $c$ had
    children, they would stay in the wrong partition too.}
\end{figure*}

### 2021-12-21 input/figundoproblem.tex
meow

\begin{figure*}
  \newcommand{\SCALE}{0.9}
  \newcommand{\LEFT}{\triangleleft}
  \newcommand{\RIGHT}{\triangleright}
  \begin{center}
    \subfloat[Part A][\label{fig:undoproblemA}$a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figundoproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:undoproblemB}$c$ deletes its partition but $a$ does not.
      $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figundoproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
             {\input{input/figundoproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers and forwards $\delta_c$.]
             {\input{input/figundoproblemD.tex}}
  \end{center}
  \caption{\label{fig:undoproblem}From $c$'s perspective, this
    scenario and Figure~\ref{fig:problem} are similar. Even when $a$
    did not delete its partition, $c$ must acknowledge $P_a$'s
    \emph{possible} deletion and propagate it.}
\end{figure*}

>>>>

\begin{figure*}
  \newcommand{\SCALE}{0.9}

  \thickmuskip=0mu
  \medmuskip=0mu
  \thinmuskip=0mu

  \newcommand\X{50pt}
  \newcommand\Y{-50pt}

  \newcommand{\OACK}{0.5}
  \newcommand{\SMSG}{\tiny}

  \newcommand{\LEFT}{\triangleleft}
  \newcommand{\RIGHT}{\triangleright}

  \begin{center}
    \subfloat[Part A][\label{fig:undoproblemA}$a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figundoproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:undoproblemB}$c$ deletes its partition but $a$ does not.
      $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figundoproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
             {\input{input/figundoproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers and forwards $\delta_c$.]
             {\input{input/figundoproblemD.tex}}
    \hspace{5pt}
    \subfloat[Part E][\label{fig:undoproblemE}$a$ echoes back $\alpha_a^2$ that $b$ needs.]
             {\input{input/figundoproblemE.tex}}
    \hspace{5pt}
    \subfloat[Part F][\label{fig:undoproblemF}$a$, $b$, and $c$ belong to $P_a$.]
             {\input{input/figundoproblemF.tex}}
  \end{center}
  \caption{\label{fig:undoproblem}From $c$'s perspective,
    Figure~\ref{fig:problemE} and Figure~\ref{fig:undoproblemE} are
    similar in terms of received messages, but the outcomes eventually
    differ. Yet, $c$ must act on Figure~\ref{fig:undoproblemE}, and
    acknowledge then propagate the \emph{possible} staleness of its
    partition $P_a$.}
\end{figure*}
